---
title: Traffic Data Analysis
output: html_document
---
```{r}
library(dplyr)
```
#Reading and looking at the data

```{r}
data <- read.csv("../all-semi-unique.csv")
names(data)
str(data)
glimpse(data)
```

#Cleaning data
We can see there is a huge number of rows which probably contain duplicates and also there are many columns with only 1 value like all the rows that starts with ad which probably means advertisment
```{r}
data <- data[!duplicated(data),]
data<-Filter(function(x)(length(unique(x))>1), data)
glimpse(data)
```
The number of rows didnt decrease however we removed columns that are not useful, and since there is a crawl date so we will try to ingore it and see what happens

```{r}
data <- data[!duplicated(data[,-1]),]
glimpse(data)
```
this didnt reduce the number of rows either,and after taking a look at the whole data file i noticed that the rd.rp.hr and rd.rp.mn change with every crawl which means its the time with respect to the crawel time,so we try to find an id,and there is a column that looks like a id, ## $ rd.rp.cmid   (int) 9300046, 9299640, 9299068, 9298351, 9300548,so we will use this column
```{r}
data <- data[!duplicated(data[,17]),]
glimpse(data)
```