---
title: Traffic Data Analysis
output: html_document
---
```{r}
library(dplyr)
library(ggplot2)
library(tidyr)
```
#Reading and looking at the data

```{r}
data <- read.csv("../all-semi-unique.csv")
names(data)
str(data)
glimpse(data)
```

#Cleaning data
We can see there is a huge number of rows which probably contain duplicates and also there are many columns with only 1 value like all the rows that starts with ad which probably means advertisment
```{r}
data <- data[!duplicated(data),]
data<-Filter(function(x)(length(unique(x))>1), data)
glimpse(data)
```
now we want to remove all columns that are images(probably ids or links) as they are not useful
```{r}
data <- data[, -grep("img$", colnames(data))]
data <- data[, -grep("Img$", colnames(data))]
glimpse(data)
```
The number of rows didnt decrease however we removed columns that are not useful, and since there is a crawl date so we will try to ingore it and see what happens
```{r}
data <- data[!duplicated(data[,-1]),]
glimpse(data)
```
this didnt reduce the number of rows either,and after taking a look at the whole data file i noticed that the rd.rp.hr and rd.rp.mn change with every crawl which means its the time with respect to the crawel time,so we try to find an id,and there is a column that looks like the comment id, ## $ rd.rp.cmid   (int) 9300046, 9299640, 9299068, 9298351, 9300548,so we will use this column
```{r}
data <- data[!duplicated(data[,16]),]
glimpse(data)
```
now first we need to put the crawel date in a better format
```{r}
data$crawl_date <- as.POSIXct(strptime(data$crawl_date,  format="%a %b %d %H:%M:%S UTC %Y", tz="UTC"))
glimpse(data)
```
now to understand both rd.rp.hr and rd.rp.mn, looking at the comment with id 9300548 in the original data,i could see that this id was found 3 times at 08:01,08:31 and 9:01 all on feb 6,their values were 23-32,24-2 and 24,32 which means its the time passed since this comment was made ,so we can subtract the time from the crawl date to get when each comment was made

```{r}
data<-Filter(function(x)(length(unique(x))>1), data)
data$comment_time <-(data$crawl_date-(data$rd.rp.hr*60*60 + data$rd.rp.mn*60))
glimpse(data)
```
#Understanding all columns
now we understand many of the columns but there are few columns that are still not clear,these are
```
rd.stid 
rd.new 
rd.strq 
rd.cmrq 
```
first i will check the possibility which is there is a road and a street and each has its own id so we will take a look at the first 100 value of each then a random 100 value
```{r}
head(data[c("rd.nm","rd.stid","rd.rp.stid")], n=100)
s<-sample_n(data,100,replace=TRUE)
head(s[c("rd.nm","rd.stid")], n=100)
```
looks like its not a street id however i can see that not all roads are road:street,but sometimes the street is missing so its better to seprate them to know exactly when a street is missing
```{r}
data <- separate (data = data,col = rd.nm, into = c("road_name","street_name") ,sep = ";")
glimpse(data)
```
rd.stid looks like rd.rp.stid which is the report status id(lazeez is 2 and 7alawa is 1) so my guess it is the total status for the road which means if it have 2 reports with id 1,2 reports with id 2 and 2 reports with id 3 the total status for this road should be 2,we can try to confirm by calculating the mean of the report status ids for a road and compare it to the road status id
```{r}
tapply(data$rd.stid , data$rd.ri, mean,na.rm=T)
tapply(data$rd.rp.stid , data$rd.ri, mean,na.rm=T)
s <- filter(data, rd.ri== 696)
tail(s[c("rd.stid")], n=50)
tail(s[c("rd.rp.stid","street_name","comment_time")], n=50)
```
as we can see the numbers here have alot of different values which 